The problem and promise of scale in multilayer networks

### 2019-09-12 paper/introduction.Rmd
it's complicated

The main types of spatial data that can be included in multilayer networks are georeferenced biologging data and *landscape scale data. * Georeferenced biologging data, including radio-frequency identification tags, radiotelemetry, and Global Positioning System (GPS) devices, provide an alternative to time and labour intensive direct observations of individuals and their interactions [@krause2011]

Land cover, land use

Edges between nodes can define individual's associations, preda

>>>>

The main types of spatial data that can be included in multilayer networks are georeferenced biologging data and landscape level data. Georeferenced biologging data, including radio-frequency identification tags (RFID), passive
integrated transponder (PIT), radiotelemetry, and Global Positioning System (GPS) devices, provide an alternative to intensive direct observations of individuals and their interactions. In addition, some animals are not easily observed, e.g.: marine mammals and birds, and these data provide an inside look. Some derived products can be generated from these data as well, including home ranges, utilization distributions and habitat patches. Landscape level data include relatively stable measures of a lanscape such as land cover, land use and elevation, and more variable measures such as temperature, precipitation and snow cover.

Given the variety of multilayer networks and types of spatial data that can be included, there are a large number of ways to combine them. Multilayer networks may be composed of categorical and unordered layers (termed 'categorical coupling'), including spatial variables such as land cover, land use, and explicit habitat patches. Multiplex networks, where each layer represents a different type of interaction, may be composed of a layer defined by an association index and another one by home range overlap. A network of networks may be used to represent communities as layers with interlayer edges defined by their spatial connectivity and intralayer edges defined by a spatially derived association index.

<!-- it's complicated -->

Spatial scale influences all of these types of spatial data and the inferences derived when combining them in a multilayer network

All biologging sensors have some spatial error

In addition, biologging sensors vary in terms of fix rate or data collection rate. GPS collars can be programmed but will inevitably vary
Temporal grouping

All remotely sensed imagery is an average of area on land, reported by the

Matching scale of imagery to resolution of fix rate

PIT tags have <1m reading distance [@krause2013]
GPS collars have challenges due to dense vegetation 
Telemetry >10m location error
